### 2023-09-04 paper/sec-dis-pseudodata.tex
Minor corrections
revision completed

Structure functions depend on both $x$ and $Q^2$, while the differential
cross-section depends also on the neutrino energy $E_\nu$, or alternatively
on the inelasticity $y$.
%
Further, structure functions $F^{\nu A}_i(x,Q^2)$ and $F^{\bar{\nu} A}_i(x,Q^2)$ depend on the nuclear target $A$ entering neutrino scattering through the
nuclear modifications of the free-nucleon PDFs.
%
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) are valid provided
the hadronic 
invariant mass $W$  is above the resonance production threshold,
\be
\label{eq:W2_invmass}
W^2 = \lp m_N^2 + Q^2 \frac{(1-x)}{x} \rp \gsim \lp 2\,{\rm GeV} \rp^2\, ,
\ee
and in addition here we  restrict ourselves to the DIS region with perturbative momentum
transfers $Q^2 \gsim 2$ GeV$^2$, such that
 structure functions can be decomposed as
\be
\label{eq:sfs_pqcd}
 F^{\nu A}_i(x,Q^2) = \sum_{j=q,\bar{q},g}\int_x^1 \frac{dz}{z}\, C_{i,j}^{\nu N}(z,\alpha_s(Q^2))f^{(A)}_j\lp \frac{x}{z},Q^2\rp \, , \quad i = 2,3,L \, .
 \ee
%
in terms of a convolution of partonic scattering cross-sections  $C_{i,j}^{\nu N}(x,\alpha_s)$ and
of process-independent PDFs $f^{(A)}_j\lp x,Q^2\rp$.
%
A similar expression holds for charm production~\cite{Faura:2020oom}, which requires
accounting also for charm mass effects~\cite{Gao:2017kkx}.
%
Here the theory pipeline adopted
to evaluate neutrino structure functions using Eq.~(\ref{eq:sfs_pqcd}) is provided by 
{\sc\small EKO}~\cite{Candido:2022tld}
and {\sc\small YADISM}~\cite{yadism,Candido:2023utz}
interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss}
for the generation of fast interpolation grids.

@@

 The calculation of differential neutrino scattering event rates
 at the LHC far-forward detectors involves two main ingredients: the energy
 and flavour dependence of the incoming neutrino flux crossing
 the detector fiducial volume, on the one hand,
 and the scattering rates within the same fiducial volume, on the other hand.
 %
 Here we summarise the main features of each of the existing and future
 far-forward detectors considered, in particular concerning
 their acceptance and expected performance.
 %
 We focus on  muon-neutrino scattering, which benefits from the highest rates and is less
 affected by theoretical uncertainties in the production mechanism, but
 provide also predictions for electron-neutrino scattering.

@@

We define the fractional uncertainty associated
to a given systematic source, say $\delta E_\ell$, for bin $i$
to be the mean of the absolute difference between the number of events in this bin for the smeared samples $\{\mathcal{D}_k\}$  and the number of events in this bin for ${\mathcal{D}_0}$ which also serves as a normalization to produce a fractional uncertainty:
\be
\delta_{\rm sys}^{(E_\ell)} =\la \left|  \frac{{N}^{(i)}_{E_\ell-{\rm smeared},k} -N_0^{(i)}}{N_0^{(i)}}\right|\ra \, .
\ee
The systematic uncertainty in event yield caused by $\delta E_\ell$ is then $\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)}$.
%
Individual sources of systematic errors are treated as uncorrelated among them, and hence
by producing samples where only one source of error is varied at a time
we can determine the systematic errors, Eq.~(\ref{eq:event_yields_systematic_error}), in each bin
for each of the considered experiments.
%
This approach has the benefit that rescaling individual sources of systematic
uncertainties, say to assess the impact of improved detector performance,
becomes straightforward.

>>>>

Structure functions depend on both $x$ and $Q^2$, while the differential
cross-section depends also on the neutrino energy $E_\nu$, or alternatively
on the inelasticity $y$.
%
Further, structure functions $F^{\nu A}_i(x,Q^2)$ and $F^{\bar{\nu} A}_i(x,Q^2)$ depend on the nuclear target $A$ entering neutrino scattering through the
nuclear modifications of the free-nucleon PDFs.
%
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) are valid provided
the hadronic 
invariant mass $W$  is above the resonance production threshold,
\be
\label{eq:W2_invmass}
W^2 = \lp m_N^2 + Q^2 \frac{(1-x)}{x} \rp \gsim \lp 2\,{\rm GeV} \rp^2\, ,
\ee
and in addition here we  restrict ourselves to the DIS region with perturbative momentum
transfers $Q^2 \gsim 2$ GeV$^2$, such that
 structure functions can be decomposed as
\be
\label{eq:sfs_pqcd}
 F^{\nu A}_i(x,Q^2) = \sum_{j=q,\bar{q},g}\int_x^1 \frac{dz}{z}\, C_{i,j}^{\nu N}(z,\alpha_s(Q^2))f^{(A)}_j\lp \frac{x}{z},Q^2\rp \, , \quad i = 2,3,L \, .
 \ee
%
 expressed
 in terms of a convolution of partonic scattering cross-sections  $C_{i,j}^{\nu N}(x,\alpha_s)$ and
of process-independent PDFs $f^{(A)}_j\lp x,Q^2\rp$.
%
A similar expression holds for charm production~\cite{Faura:2020oom}, which requires
accounting also for charm mass effects~\cite{Gao:2017kkx}.
%
Here the theory pipeline adopted
to evaluate neutrino structure functions using Eq.~(\ref{eq:sfs_pqcd}) is provided by 
{\sc\small EKO}~\cite{Candido:2022tld}
and {\sc\small YADISM}~\cite{yadism,Candido:2023utz}
interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss}
for the generation of fast interpolation grids.

@@

 The calculation of differential neutrino scattering event rates
 at the LHC far-forward detectors involves two main ingredients: the energy
 and flavour dependence of the incoming neutrino flux crossing
 the detector fiducial volume, on the one hand,
 and the scattering rates within the same fiducial volume, on the other hand.
 %
 Here we summarise the main features of each of the existing and future
 far-forward detectors considered, in particular concerning
 their acceptance and expected performance.
 %
 We focus on  muon-neutrino scattering, which benefits from the highest rates and is less
 affected by theoretical uncertainties in the production mechanism, but
 provide also predictions for the subdominant electron-neutrino structure functions.

@@

We define the fractional uncertainty associated
to a given systematic source, say $\delta E_\ell$, for bin $i$
to be the mean of the absolute difference between the number of events in this bin for the smeared samples $\{\mathcal{D}_k\}$  and the number of events in this bin for ${\mathcal{D}_0}$ which also serves as a normalization to produce a fractional uncertainty:
\be
\delta_{\rm sys}^{(E_\ell)} =\la \left|  \frac{{N}^{(i)}_{E_\ell-{\rm smeared},k} -N_0^{(i)}}{N_0^{(i)}}\right|\ra \, .
\ee
The absolute systematic uncertainty in event yield caused by $\delta E_\ell$ is then $\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)}$.
%
Individual sources of systematic errors are treated as uncorrelated among them, and hence
by producing samples where only one source of error is varied at a time
we can determine the systematic errors, Eq.~(\ref{eq:event_yields_systematic_error}), in each bin
for each of the considered experiments.
%
This approach has the benefit that rescaling individual sources of systematic
uncertainties, say to assess the impact of improved detector performance,
becomes straightforward.
